Computer Science House Constitution

### 2024-03-05 constitution.tex
Rebase off of current master branch (#96)
Co-authored-by: Sam Cordry <samcodry@gmail.com>

Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an E-Board member.
A voting E-Board member is considered to be any person with a non-zero vote on E-Board. % Defined this way so that (for example) each member in a dual directorship is each considered to be a voting member on E-Board.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House.

@@

\asubsubsection{Responsibilities of Ad Hoc Directorships}
\begin{enumerate}
	\item Ad Hoc Directorships are responsible for the task for which they were created
	\item Any responsibilities budgets or finances for the Ad Hoc Directorship are placed upon the assigned director
\end{enumerate}

@@

\asubsubsection{Qualifications to be the House Secretary or an Ad Hoc Director}
\begin{enumerate}
\item Candidates must be Active Members
\end{enumerate}

@@

If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot.
If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative.
Each different nomination must be a separate entry on the election ballot.
Non-voting E-Board positions (i.e. Ad Hoc Directors) are not restricted to single or dual directorship.

@@

>>>>

Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an E-Board member.
A voting E-Board member is considered to be any person with a non-zero vote on E-Board. % Defined this way so that (for example) each member in a dual directorship is each considered to be a voting member on E-Board.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House.

@@

@@

\asubsubsection{Qualifications to be the House Secretary}
\begin{enumerate}
\item Candidates must be Active Members
\end{enumerate}

@@

If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot.
If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative.
Each different nomination must be a separate entry on the election ballot.

@@

\asection{Ad Hoc Directorships}
Ad Hoc Directorships are created by the Executive Board on an as-needed basis.
They are generally task-oriented and are chaired by a House member(s).
Ad Hoc Directors are responsible for the task for which they were created.
Additionally, any responsibilities, budgets, or finances for the Ad Hoc Directorship are placed upon the assigned director(s).
Candidates for being Ad Hoc Directors must be Active Members.
% This is implied, but Ad Hoc Directorships are not intended to be restricted to single or dual directorship rules.
